CDSR Human Data/Modelling Paper

### 2013-09-08 scenarios/cdsr/trunk/papers/ACS2013/main.tex
JK added results of t-tests for likert scale results

Trial 2
Trial 3

>>>>

The type 2 trials the same visual stimuli and accompanying spatial descriptions as the type 1 trials with the addition that a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region. For each stimuli domain (classroom, map, military engagement) three points were pre-selected such that for each particular stimuli one of the points was located near the expected prototypical center of the described spatial region and the other two points were at varying distances from this location. For clarity it is worth emphaising that, although the same three points were used for all the stimuli from a particular domain, the particular point that acted as the sweetspot for a particular stimuli within a domain set would vary from stimuli to stimuli. The selection of these points was informed by the results of a pilot study. Figure \ref{fig:locations} illustrates the points selected for each domain and overlays them on one of the visual stimuli from each domain. Table \ref{tab:point-likert-scores} list the average likert scores for the different points in each domain. In the map domain the points are named from top-left to bottom-right (e.g., $Pt1$ is the point in the top left of Figure \ref{fig:bottleneck-points}); in the classroom domain the points are named in order from left to right (e.g. $Pt1$ is the leftmost point marked in Figure \ref{fig:classromm-points}); and, in the military engagment domain the points are named from top to bottom (e.g., $Pt1$ is the point nearest the top of Figure \ref{fig:tanks-points}). For each stimuli we have highlighted in bold the maximum average likert rating for a point for that stimuli.

\begin{figure}
%\includegraphics[width=0.4\textwidth]{figures/turrets-plus-one.jpeg}
\centerline{
\begin{tabular}{ccc}
\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/classroom-circle-points.png}\caption{}\label{fig:classroom-points}\end{subfigure}&
\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/bottleneck-2-points.png}\caption{}\label{fig:bottleneck-points}\end{subfigure}&
\begin{subfigure}[b]{0.3\textwidth}\includegraphics[width=\textwidth]{figures/tanks-close-points.png}\caption{}\label{fig:tanks-points}\end{subfigure}\\
\end{tabular}
}
\caption{The pre-selected locations for each domain used in the Type 2 Trials.}
\label{fig:locations}
\end{figure}

\begin{table}
\centerline{
\begin{tabular}{l c c c l}
\hline
Domain & \multicolumn{4}{c}{Map/Bottleneck} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot Rated Significantly Higher? \\
Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
(g) & $1.1707$ & $\mathbf{4.6667}$ & $1.85$ & $H_A:\mu(P2)>\mu(P1),~p<2.2^{-16};~H_A:\mu(P2)>\mu(P3),~p<2.2^{-16}$\\ % 1_1
(h) & $1.1707$ & $\mathbf{4.7561}$ & $1.585$ & $H_A:\mu(P2)>\mu(P1),~p<2.2^{-16};~H_A:\mu(P2)>\mu(P3),~p<2.2^{-16}$\\ % 1_2
\hline
Domain & \multicolumn{4}{c}{Classrom/Front of Room} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot Rated Significantly Higher? \\
Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ & $H_A:\mu(P1)>\mu(P2),~p=6.497^{-4};~H_A:\mu(P1)>\mu(P3),~p=4.073^{-8}$\\ % 2_1
(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ & $H_A:\mu(P1)>\mu(P2),~p=6.396^{-16};~H_A:\mu(P1)>\mu(P3),~p<2.2^{-16}$\\ % 2_6
(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ & $H_A:\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p:1.864^{-12}$\\ %2_7
(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ & $H_A=\mu(P1)>\mu(P2),~p<2.2^{-16};~H_A=\mu(P1)>\mu(P3):~p<2.2^{-16}$\\ %2_2
(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2):~p<2.2^{-16}$\\ % 2_3
(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ & $H_A=\mu(P1)>\mu(P2),~p<2.2^{-16};~H_A=\mu(P1)>\mu(P3),~p<2.2^{-16}$\\ % 2_4
(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p<2.2^{-16}$\\\\ % 2_5
\hline
Domain & \multicolumn{4}{c}{Military Engagement/Safe Region} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} &  Sweetspot Rated Significantly Higher?\\
Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
(i) & $1.1951$ & $4.3902$ & $\mathbf{4.9024}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=5.382^{-4}$\\ % 3_1
(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p<7.981^{-14}$\\ % 3_2
(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=2.708^{-13}$\\ % 3_3
(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=6.621^{-12}$\\ % 3_4
\hline
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Average Likert Ratings per Point by Domain with T-Test results: in all cases the average rating of the sweetspot is significantly higher than the other points tested for that stimuli}
\end{table}

\begin{table}
\centerline{
\begin{tabular}{c c c c }
\hline
Domain & \multicolumn{3}{c}{Classrom/Front of Room} \\
$H_0$ & $H_A$ & $\alpha$ & p-value\\
$\mu(c.P1)=\mu(c-flipped.P3)$ & $\mu(c.P1)!=\mu(c-flipped.P3)$ & $0.05$ & $0.6315$\\
$\mu(e.P1)=\mu(e-flipped.P3)$ & $\mu(e.P1)!=\mu(e-flipped.P3)$ & $0.05$ & $0.7358$\\
$\mu(f.P1)=\mu(f-flipped.P3)$ & $\mu(f.P1)!=\mu(f-flipped.P3)$ & $0.05$ & $0.2592$\\
\hline
\hline
\end{tabular}
}
\label{tab:flipped-point-likert-scores}
\caption{Two Tailed Two Sample T-Tests for flipped stimuli pair trials.}
\end{table}
